\addchap*{Abstract}
\label{abstract}
{\LARGE Visualization Verification of Complex Avionic Models Using Computer Vision}

With the increasing complexity of models and applications in aviation, the use of domain specific modeling (DSM) in the field has become vital. DSM enables engineers to work more efficiently and reduce errors in generated code through automation. However, for use in safety-critical applications, DSM requires significant effort, particularly in ensuring correct model visualizations to reduce the amount of manual verification work.

This thesis aims to build upon the work of \cite{og_paper} to improve the reliability of the automated verification of block-diagram visualizations in DSM. In \cite{og_paper}, the computer vision library \textit{Open Computer Vision} or \textit{OpenCV} was used to recognize and process block diagram models. The results were compared with the original model to find and indicate deviations to the user inside a browser-based graphical model editor called \textit{eXtensible Graphical EMOF Editor} or \textit{XGEE}.
The original implementation of the block diagram recognition algorithm was limited in its ability to process complex and diverse diagrams within XGEE.

This thesis extends the capabilities of the block diagram recognition algorithm to work with complex and diverse diagrams in three seperate graphical domain-specific languages within XGEE. The new implementation is able to correctly identify and process intersecting or partially obscured connecting edges in any orientation, detect a larger variety of overlapping vertices of differing sizes and shapes and process text labels in multiple orientations, showcasing its potential to significantly reduce manual verification effort in DSM applications.